% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Personal Projects}{\faLaptop}

\begin{projects}
	\project
	{Campervan Conversion - Hyundai iLoad}{2023 - Current}
	{TBA}
	{I have taken on the task of designing and converting a Hyundai iLoad into a campervan from scratch. A project like combines the love I have for implementing awesome ideas and my sense of outdoor adventures.
	Fitting out my iLoad has allowed me to flex my hands on practical abilities and challenged my creative side}
	{Design, Idea Formulation, Problem Solving, Cabnet Making}

	\project
	{Advent Of Code}{2021 \& 2022}
	{\github{Prelly95/AOC2021}\github{Prelly95/AOC2022}}
	{I have long since been interested in the Rust paradigm and I've dabbled with a few projects here and there. I like to have a crack at some advent of code problems over each Christmas break.}
	{Rust, Logic}

	\project
	{Two-wheeled balancing robot}{2017}
	{\github{Prelly95/MCHA3K}}
	{Design and development of a self-balancing two-wheeled robot – this required
	implementation of full state feedback control with a Kalman filter observer @50Hz and was constrained by the
	hardware of an Atmel ATMega32.}
	{PCB / Circuit Design, Embedded C, Matlab, State Feedback, Eagle}

	\project
	{Borne Clothing}{2019 - Current}
	{\sociallink{\faLink}{https://www.borneclothing.com/}{borneclothing.com}}
	{Co-founder and Chief Technical Officer of Borne Clothing, an e-commerce social enterprise that creates sustainably sourced and ethically made mosquito-repellent clothing. We commit to donating 50\% of our profit to fund public health interventions that tackle mosquito-borne diseases. My role includes back-end website development and interpreting customer and marketing data to facilitate lean growth.}
	{Business Management, Community Development, Social Impact}

\end{projects}